\hyperlink{classNeuron}{Neuron} project S\-V\-B\-A3 A. Program presentation\-: The Introduction to this project is in src/html/index.\-html

B. Program compilation In the terminal, go to src. 1-\/ Type in \char`\"{}cmake ..\char`\"{} 2-\/ Type in \char`\"{}make\char`\"{} To launch overall program with 12500 neurons\-: 3-\/ Type in \char`\"{}./\-All\-Neurons\char`\"{} and set the simulation time to 100 (ideal). To launch google tests\-: 3-\/ Type in \char`\"{}./googletests\char`\"{}

C. Program Uses This program is based on the \char`\"{}\-Brunel\char`\"{} paperwork. All constants are in \char`\"{}src/\-Utility/\-Constants.\-hpp\char`\"{}.

For H\-T\-M\-L documentation\-: -\/index.\-html is the introduction to this project. -\/class\-Network.\-html documents the class \hyperlink{classNetwork}{Network}. -\/class\-Neuron.\-html documents the class \hyperlink{classNeuron}{Neuron}. -\/class\-Neuron/\-Network-\/members.\-html contains all member functions of respective class. -\/files.\-html gives access to both classes. -\/\-Class variables can be accessed with functions\-\_\-vars.\-html -\/\-Source documents can be accessed with Network/\-Neuron\-\_\-8hpp\-\_\-source.\-html

In the directory \char`\"{}\-Plots\char`\"{} are plots with different g and eta values to illustrate Figure 8 a to d in the \char`\"{}\-Brunel\char`\"{} paperwork. All files \char`\"{}...\-\_\- file1\char`\"{} have been generated with gnuplot. Gnuplot can be launched from terminal by writing\-: 1-\/ gnuplot 2-\/ plot \char`\"{}spikes.\-txt\char`\"{} using 1\-:2 with boxes All files \char`\"{}...\-\_\- file2\char`\"{} have been generated using an online plotter\-: \href{https://cs116-plot.antoinealb.net/}{\tt https\-://cs116-\/plot.\-antoinealb.\-net/}.

To run the test with one neuron, type ./\-One\-Neuron To run the test of the buffer with two neurons, type ./\-Buffer Please note that the file entitled \char`\"{}jupyterplot\char`\"{} will in this case contain the membrane potential of each neuron, therefore being able to observe the delay installed by the buffer. 